Gurusharan Kunusoth
## 1. Ethanol
## 1a.
```{r}
rem = c(63, 54, 69, 50, 72,45, 60, 40, 56,31, 40, 45, 25, 23,28)

treatments = c(1,1,1,1,1,2,2,2,2,3,3,3,3,3,3)

treatments = as.factor(treatments)

boxplot(rem~treatments,xlab="Treatments",ylab="REM")
```




My intuition tells me that ANOVA will reject $H_0$ since the mean REM sleep time seems to be different in each treatment sample.

## 1b.
```{r}
aov.out = aov(rem~treatments)
aov.out
summary(aov.out)

```


## 1c.
```{r}
qqnorm(rem,pch=16)
plot(aov.out)
```




As, the graph is linear, the normality condition is satisfied.

The residual plot is created by the command plot(aov.out). As there is no specific pattern , constant variance condition is also satisfied.




## 1d.

As the p-value is less than 0.05, we reject the null hypothesis and conclude that the effect of treatments on amount of REM sleep is significant.



## 1e.

```{r}
TukeyHSD(aov.out)
plot(TukeyHSD(aov.out))
```
Treatment 1 and treatment 3 population means are different and Treatment 2 and Treatment 3 population means are different since both the CIs associated with the differences of these populations exclude 0
