Gurusharan Kunusoth

# 1. Spiders
## 1a.

```{r}
speed=c(1.25, 1.64, 1.91, 2.31, 2.37, 2.38, 2.84, 2.87, 2.93, 2.94, 2.98, 3.00, 3.09, 3.22, 3.41)
hist(speed)
```

## 1b.

```{r}
mean(speed)
sd(speed)
```
Mean indicates the average of the speeds which is 2.609333. 
Standard deviation is a measure of how dispersed the data is in relation to the mean. Here, the standard deviation is  0.6178473

## 1c.

```{r}
q=quantile(speed)
q1=q[2]
q2=q[3]
q3=q[4]
q1
q2
q3

```
Yes, both the answers match.

## 1d.

```{r}
IQR(speed )
```


## 1e.

```{r}
boxplot(speed)
```


# 2. Two histograms
## 2a.
Sample A is larger

## 2b.
Sample B has larger standard deviation

## 2c.
The second, which has the the same x-axis limits for samples A and B.

# 3. Circuit board
## 3a.
0.675

## 3b.
0.3

# 4. Fruit flies
0.58

# 5. Dice
## 5a.
1/6

## 5b.
1/6

## 5c.
1/18

## 5d.
P(A and B) and P(A) × P(B) are not equal. So, A and B are not independent.

## 5e.
1/3

## 5f.
P(A|B)=1/3 
[P(A and B)]/P(B)=1/3
Hence, they are equal.




