Gurusharan Kunusoth



## 1 Pumpkins
## 1a.

```{r}
x=c(9.6, 8.8, 5.1, 9.7, 9.1, 8.9, 8, 9.2, 2.7, 9.1, 8.5, 7.3, 9.3, 9.6, 4.1, 9.9, 7.6, 9, 7.2, 8.5)

qqnorm(x, pch=1, frame=FALSE)
qqline(x, col="blue", lwd=1)
```

According to the QQ plot, it is not reasonable to assume that the population is normal because the points are not closely aligned with the line.

## 1b.

```{r}
conf=0.90
alpha=1-conf
B=2000
bm={}
for(i in 1:B){
  set.seed(i)
  bm[i]=mean(sample(x,20,replace=TRUE))
}
ci=quantile(bm,c(alpha/2,1-alpha/2))
ci
```
90% confidence interval for the mean is (7.35,8.68)

## 1c.


i)p-value=0.039
ii) Since, P-value<α, this data is strong evidence that the mean pumpkin is greater than 7.2

## 1d.

1.9468

## 1e.

0.0323

## 1f.

since,p-value < α, We  reject null hypothesis(Ho)
there is strong evidence that the true median weight for this pumpkin farmer’s patch is greater than 7.2.

## 2. Penguins
## 2a.

0.4

## 2b.

0.1096

## 2c.

(0.1852,0.6148)

## 2d.

P value = 0.0332

since p value < 0.05, the result is significant

We reject the null hypothesis that \pi=0.63

At 0.05 level, the data provided strong evidence that proportion of female is diffrent from 0.63
