Gurusharan Kunusoth

## 1. Oximeters
## 1a.

98% confidence interval for the true difference in mean readings from the two oximeters is 1.717 to 2.683

## 1b.
p-value=0, and since p=0<0.02, it is concluded that the null hypothesis is rejected.

Null hypothesis Ho is rejected. Therefore, there is enough evidence to claim that the population mean μ_1 is different than μ_2, at the α=0.02 significance level.


## 2. Dairy
## 2a.

```{r}
Old_Diet= c(43, 51, 44, 47, 38, 46, 40, 35)
New_Diet= c(47, 75, 85, 100, 58)
hist(Old_Diet, xlim=c(0,100))
hist(New_Diet, xlim=c(0,100))
qqnorm(Old_Diet)
qqline(Old_Diet)
qqnorm(New_Diet)
qqline(New_Diet)
```

I chose histogram to see the difference in mean and qqplot to see if the samples can be assumed from a normal population.
From the qqplots, we can say that both fo them are from normal population.


## 2b.

```{r}
sd(Old_Diet)
sd(New_Diet)
mean(Old_Diet)
mean(New_Diet)
```


Standard deviation of old diet=5.18
Standard deviation of new diet=21.1

test statistic=-3.12
degree of freedom= 4.3
p-value=0.035
p-value<0.05
So, we can say that the milk produced by using new diet is significantly different form old one.

